Linear response theory for core set identification

### 2012-07-27 writedown/linear.response/langevin.tex
add non-linear response code. Fix bug in text

  M_j(\eta)\,\vect D(\vect X_\eta)\cdot\dd\vect W_\eta\\\label{eqn:H00}

@@

  M_j(\eta)\,M_k(\eta)\,\vect D^2(\vect X_\eta)\cdot\dd \eta

@@

>>>>

  \vect D(\vect X_\eta)\cdot\dd\vect W_\eta\\\label{eqn:H00}

@@

  \vect D^2(\vect X_\eta)\cdot\dd \eta

@@

  O[\vect X_s]\tilde O[\vect X_\eta]
  \big\rangle_{0,t,\tau}^{i-1}
  \int_{\mc\{\vect v, 0; \vect u, t\}}
  \dd\mathcal P^\beta_{i-1}[\vect X_s]
  \,
  O[\vect X_s]
  \int_{\mc\{\vect u, 0; \tau\}}
  \dd\mathcal P^{2\beta}_{i-1,t}[\vect X_\eta]
  \,
  \tilde O[\vect X_\eta]
  O[\vect X_s]
  \big\rangle_{0,t,\tau}^{i-1}
  = &\,
  \int_{\mc\{\vect v, 0; t\}}
  \dd\mathcal P^\beta_{i-1}[\vect X_s]
  \,
  O[\vect X_s]  
Then the approximated \eqref{eqn:pert-exact-1} is
  \big\rangle_{0,t,\tau}^{i-1}
  \\ \nonumber
  &\, +
  \Delta F_e^{i-1}(t) 
  \big\rangle_{0,t,\tau}^{i-1}
  \Delta s_j^{i-1}
  \big\rangle_{0,t,\tau}^{i-1}
  \big\rangle_{0,t,\tau}^{i-1}
  \frac 12
  \Delta s_j^{i-1}\Delta s_k^{i-1}
  \big\rangle_{0,t,\tau}^{i-1}
  \\\label{eqn:pert-approx-1}
  \Delta F_e^{i-1}(t) \Delta s_j^{i-1}
  G_0[\vect X_\eta]\,
  \big\rangle_{0,t,\tau}^{i-1}
The first line on the r.h.s. of \eqref{eqn:pert-approx-1}
is the zeroth order approximation,  the second line is the
first order approximation, and the last two lines are the
second order approximation.
And the approximated \eqref{eqn:pert-exact-2} is
  \nonumber
  K_{\sigma,\vect y}(\vect X_t)
  \big\rangle_{0,t}^{i-1}
  \\ \nonumber
  \Delta s_j^{i-1}
  \big\rangle_{0,t}^{i-1}
  \\\label{eqn:pert-approx-2}
  \frac 12
  \Delta s_j^{i-1}\Delta s_k^{i-1}
  \big\rangle_{0,t}^{i-1}  
The first, second and third line on the r.h.s. of \eqref{eqn:pert-approx-2}
are the zeroth order, first order and second order approximations, respectively.
